---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "Using Aggregated Polling Data to Predict the Outcome of the 2024 Presidential Race"
author: 
  - Andy Jiang
  - Onon Burentuvshin
  - Rui Hu
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
date: today
date-format: long
abstract: "The 2024 U.S. presidential election is shaping up to be a highly competitive race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome. This paper aims to build a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election. The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions. Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process. The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts. Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(readr)
library(here)
library(knitr)
library(kableExtra)


data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
```


# Introduction
The 2024 U.S. presidential election is shaping up to be one of the most closely watched and potentially pivotal elections in recent history. As public opinion shifts and political dynamics evolve, polling data has emerged as a critical tool for forecasting the outcome and understanding voter preferences. Polls provide a snapshot of where candidates stand at various points in time, reflecting the impact of campaigns, debates, and major events. However, the reliability and accuracy of individual polls can vary significantly based on methodology, sample size, and other factors, making it necessary to aggregate multiple sources of data for a more robust prediction.

This paper aims to forecast the outcome of the 2024 U.S. presidential election by leveraging a "poll-of-polls" approach, which aggregates data from various pollsters to create a more comprehensive picture of the race. By focusing on high-quality polls and conducting a detailed analysis of the polling trends for the two main candidates, Donald Trump and Kamala Harris, we seek to uncover patterns in voter support and potential factors influencing shifts in public opinion. Additionally, the paper examines the methodologies of different pollsters to assess their strengths and weaknesses, which can help identify possible biases in the aggregated data.

The analysis will further explore the geographic distribution of support across key battleground states, providing insights into the electoral landscape. Finally, the paper presents an idealized polling methodology with a $100,000 budget, designed to improve the accuracy and representativeness of election forecasts. By integrating multiple data sources and critically evaluating polling practices, this study aims to contribute to the ongoing discussion on the role of polling in democratic processes and election forecasting.



# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].

## Measurement
	
Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.


```{r}
#| echo: false
#| warning: false
#| message: false

# Set seed for reproducibility
set.seed(316)

sample_data <- data %>% sample_n(10)

# Display the sampled data as a table with smaller text
kable(sample_data, caption = "Sample of 10 Random Observations from the Analysis Data") %>%
  kable_styling(font_size = 8)  # Adjust the font size as needed
```


```{r}

```


## Predictor variables







# Model



## Model set-up


### Model justification



# Results


```{r}
#| echo: false
#| warning: false
#| message: false
data_filtered <- data %>% filter(candidate_name %in% c("Donald Trump", "Kamala Harris"))

# Now proceed with calculating the average polling percentage by state
data_avg <- data_filtered %>%
  group_by(state, candidate_name) %>%
  summarize(avg_pct = mean(pct, na.rm = TRUE))

# Plotting the average polling percentages by state
ggplot(data_avg, aes(x = reorder(state, avg_pct), y = avg_pct, fill = candidate_name)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Average Polling Percentages by State",
       subtitle = "Comparing Support for Trump and Harris Across States",
       x = "State",
       y = "Average Polling Percentage",
       fill = "Candidate") +
  coord_flip() +  # Flip coordinates for easier reading
  theme_minimal()
```

```{r}

```




# Discussion

## First discussion point {#sec-first-point}



## Second discussion point


## Third discussion point

## Weaknesses and next steps


\newpage

\appendix

# Appendix {-}
Sampling Methodology Employed by New York Times and Siena College:

	Our analysis and prediction utilizes data collected by a single pollster and it is important to scrutinize the sampling methodology behind the sampling methods used to determine the extent of the external validity of our predictions. Primarily, the data gathered by New York Times was done so with the collaboration with Siena College through live-interviewers reaching voters by telephone. 
	The poll targets registered voters in the United States, with a particular focus on voters in battleground states for presidential races. Although this focus is emphasized and accounted for, their target population is the population of registered voters in the United States of America. The sampling frame is the voter file, a comprehensive database of registered voters that includes demographic information, voting history, and contact details. And from this sampling frame, respondents are randomly selected, balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population. 
	The poll relies on random digit dialing to reach voters, predominantly via cellphones (over 90% of calls). While landlines are also called, the dominance of cellphone usage aligns with contemporary communication trends. This results in their rendition of random sampling, which contributes to the external validity of proper usage of data. However, though the sample was selected randomly, reaching voters by phone has become more difficult due to low response rates (around 2%), requiring many attempts to secure responses from certain individuals. Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states. This also raises the concern of selection bias as younger voters that display a propensity for digital communication might be underrepresentted. 
	The poll addresses non-response through a combination of front-end sampling adjustments (calling harder-to-reach voters) and post-survey weighting. Weighting is applied to ensure that the final sample aligns with the demographic and political composition of the electorate, based on voter file data. Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond. Experiments with alternative methods, such as mail surveys, have shown some differences, particularly in political engagement levels, but not in overall vote preferences.


	
Sampling Approach: Stratified Sampling

Method: Stratified sampling is used, where different voter groups are targeted based on their demographic and regional characteristics. For battleground state polls, the sample is drawn from states likely to decide the election, such as Arizona, Georgia, and Pennsylvania.

Trade-offs: While phone polling allows for broad geographic reach and is quick to execute, it faces declining response rates and potential underrepresentation of certain groups. The reliance on phone surveys limits the ability to reach voters without reliable phone access, and it may inadvertently bias results towards those who are more reachable by phone.


Questionnaire

The Times/Siena Poll carefully crafts its questions to be fair and balanced, ensuring that respondents from across the political spectrum feel their views are represented. The team devotes significant time to wording questions to avoid leading respondents or introducing bias.
The questionnaire is kept relatively short (under 15 minutes), helping to reduce respondent fatigue and minimize dropout rates during the interview. Phone polls may not capture the full nuance of voter opinions due to the limited nature of phone conversations compared to online or face-to-face methods. Furthermore, telephone-based interviews with voters presents the danger of selection bias discussed earlier. As a result, while the poll's margin of error for the overall population is typically 3 to 4 percentage points, smaller subgroups may have larger margins of error due to smaller sample sizes.


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check


```{r}

```

## Diagnostics


```{r}

```



\newpage


# References


